The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study

### 2021-12-31 paper.tex
update

% After projection the photon flux at energy $$ is computed ..

\begin{equation}
I = \frac{1}{\epsilon_{1}}\int \frac{dE}{dtd\epsilon_{1}dV} dl,
\end{equation}

\subsubsection{Hadronic process}

\begin{equation}
  \frac{dE}{dtd\epsilon_{1}dV} = cn_{H}pC\left(\frac{\epsilon_{1}}{m_{\text{p}}c^2}\right)^{-p}\int_{0}^{1}\sigma(\epsilon_{\text{p}}) F(x,\epsilon_{\text{p}}) x^{p}dx.
\end{equation}

>>>>

To evaluate the photon flux at the energy $\epsilon_{1}$ and\
take into account the perspective projection effect,
we integrate the emissivity along line-of-sights from the solar position:
\begin{equation}
I = \frac{1}{\epsilon_{1}}\int \frac{dE}{dtd\epsilon_{1}dV} dl,
\end{equation}

\subsubsection{Hadronic process}
\begin{equation}
  \frac{dE}{dtd\epsilon_{1}dV} =\
   cn_{H}pC\left(\frac{\epsilon_{1}}{m_{\text{p}}c^2}\right)^{-p}\
   \int_{0}^{1}\sigma(\epsilon_{\text{p}}) F(x,\epsilon_{\text{p}}) x^{p}dx.
\end{equation}
